---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# instaloadeR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/instaloadeR)](https://CRAN.R-project.org/package=instaloadeR)
<!-- badges: end -->

The goal of `instaloadeR` is to provide a scraper for the image-sharing social networking service [Instagram](http://https://www.instagram.com/). Mostly inspired by this Scraping Tool: [digitalmethodsinitiative/4cat](https://github.com/digitalmethodsinitiative/4cat). Wraps this Python module [instaloader](https://github.com/instaloader/instaloader). You will need Python 3.6 or higher to use `instaloader`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r eval = F}
# install.packages("devtools")
devtools::install_github("favstats/instaloadeR")
```

Load library

```{r example}
library(instaloadeR)

```

Install necessary Python libraries

```{r, eval = F}
install_instaloadeR()
```


## Example

This is a basic example which shows you how to solve a common problem:

Make sure to use your preferred Python installation

```{r}
library(reticulate)

use_python(py_config()$python)

```

Initialize `instaloadeR`

```{r}
readr::write_lines(py_instaloader, "script.py")
reticulate::source_python("script.py")
```

### Get Posts with Hashtag

Return a tibble with 10 Instagram posts that use `#coronavirus`.


```{r, eval = F}

billgates <- insta_posts(query = "coronavirus", 
                         scope = "hashtag",
                         max_posts = 10, 
                         scrape_comments = F)



```
