---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# instaloadeR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/instaloadeR)](https://CRAN.R-project.org/package=instaloadeR)
<!-- badges: end -->

The goal of instaloadeR is to ...

The goal of `tiktokr` is to provide a scraper for the video-sharing social networking service [TikTok](http://tiktok.com/). Mostly inspired by this Python module: [davidteather/TikTok-Api](https://github.com/davidteather/TikTok-Api). You will need Python 3.6 or higher to use `tiktokr`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r eval = F}
# install.packages("devtools")
devtools::install_github("favstats/instaloadeR")
```

Load library

```{r example}
library(instaloadeR)

```

Install necessary Python libraries

```{r, eval = F}
install_instaloadeR()
```


## Example

This is a basic example which shows you how to solve a common problem:

Make sure to use your preferred Python installation

```{r}
library(reticulate)

use_python(py_config()$python)

```

Initialize `instaloadeR`

```{r}
init_instaloadeR()

```

### Get Posts with Hashtag

Returns a tibble with hashtags.


```{r, eval = F}

billgates <- insta_posts(query = "billgatesisevil", 
                         scope = "hashtag",
                         max_posts = 5, 
                         scrape_comments = F)



```
