---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# instaloadeR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/instaloadeR)](https://CRAN.R-project.org/package=instaloadeR)
<!-- badges: end -->

The goal of `instaloadeR` is to provide a scraper for the image-sharing social networking service [Instagram](http://https://www.instagram.com/). Mostly inspired by this Scraping Tool: [digitalmethodsinitiative/4cat](https://github.com/digitalmethodsinitiative/4cat). Wraps this Python module [instaloader](https://github.com/instaloader/instaloader). You will need Python 3.6 or higher to use `instaloader`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r eval = F}
# install.packages("devtools")
devtools::install_github("favstats/instaloadeR")
```

Load library

```{r example}
library(instaloadeR)

```

Make sure to use your preferred Python installation

```{r}
library(reticulate)

use_python(py_config()$python)

```

Install necessary Python libraries

```{r, eval = F}
install_instaloadeR()
```


## Example

This is a basic example which shows you how to solve a common problem:



Initialize `instaloadeR`

```{r, eval=F}
init_instaloadeR()
```

### Get Posts with Hashtag

Return a tibble with 10 Instagram posts that use `#coronavirus`.


```{r, eval = F}

corona <- insta_posts(query = "coronavirus", 
                         scope = "hashtag",
                         max_posts = 10, 
                         scrape_comments = F)


corona
```

Also return comments and replies to comments for the 10 last `#coronavirus` posts.

```{r, eval = F}
corona_comments <- insta_posts(query = "coronavirus", 
                         scope = "hashtag",
                         max_posts = 10, 
                         scrape_comments = T)

corona_comments
```


### Get Posts from a Specific User

Return a tibble with the 10 Instagram posts by `francediplo`.


```{r, eval = F}

francediplo <- insta_posts(query = "francediplo", 
                         scope = "username",
                         max_posts = 10, 
                         scrape_comments = F)


francediplo
```

Retrieve comments as well:

```{r, eval = F}

francediplo_comments <- insta_posts(query = "francediplo", 
                         scope = "username",
                         max_posts = 10, 
                         scrape_comments = T)


francediplo_comments
```


## Save output to csv

As function scrapes, the data is saved and continously appended to a `.csv` file (for when you have long scraping tasks). Just specify a path for the `save_path` argument.

```{r, eval = F}
francediplo_comments <- insta_posts(query = "francediplo", 
                         scope = "username",
                         max_posts = 10, 
                         scrape_comments = T, 
                         save_path = "francediplo.csv")


readr::read_csv("francediplo.csv")



```


## Get User or Hashtag posts in specific timerange

Just specify both an argument for `since` (latest date) and `until` (earliest date) and get Instagram posts in specific timerange.

```{r, eval = F}

covidgoodnews <- insta_posts(query = "covidgoodnews",
                         scope = "username",
                         max_posts = 10,
                         scrape_comments = F,
                         since = "2020-06-01",
                         until = "2020-01-01")



covidgoodnews
```


## Login with your Instagram account

Some functionalities (like scraping followers from an account) are only available if you login with your Instagram account. For this purpose, `instaloadeR` functions will read from your environment variables. 



In order to add the info to your environment file, you can use the function `edit_r_environ()` from the [`usethis` package](https://usethis.r-lib.org/).

```{r, eval = F}
usethis::edit_r_environ()
```


This will open your .Renviron file in your text editor. Now, you can add the following line(s) to it:

```{r, eval = F}
INSTAGRAM_LOGIN=YOUR_USERNAME
INSTAGRAM_PW=YOUR_PW
```

Save the file and restart R for the changes to take effect.

The password line is optional and can also be provided via a prompt which will appear if you run `insta_login` without specifying the `passwd` argument (if you are icky about typing out your password which you should always be).

Now you can use `insta_login` in the following way:

```{r, eval=F}
insta_login(save = T)
```

`save = T` will save your credentials, so next time you can just do `load = T` and you don't need to specify your password again:

```{r, eval=F}
insta_login(load = T)
```

## Get followers of an account

You can all followers of an Instagram account with `get_followers` but only if you are logged in as an Instagram user. The function `get_followers` retrieves a character vector with all usernames that follow the specified account.

```{r, eval=F}
insta_login(load = T)


get_followers("willsmith_fan_")
```


## TODO

+ Geotags
+ Download Images/videos
+ ...


